Data Exploration: IUCN and AquaMaps

### 2015-11-25 data_explore.Rmd
cleaning up data_explore and graphs

lm_eqn2 <- function(df){
  m  <- lm(area_ratio ~ sm_perc, spp_list)
  eq <- substitute(italic('y') == a + b %.% italic('x')*","~~italic(r)^2~"="~r2, 
        list(a  = format(coef(m)[1], digits = 2), 
             b  = format(coef(m)[2], digits = 2), 
             r2 = format(summary(m)$r.squared, digits = 3)))
  as.character(as.expression(eq))             
}

@@

  ggsave(filename = file.path(dir_fig, sprintf('rangemap_%s_%s.png', spp_quad, str_replace(tolower(spp), ' ', '_'))),
         plot = spp_plot, 
         width = 8, height = 4, dpi = 200)
}

@@

Plotting species from q1 (well-matched)
```{r plot_spp_from_q1, echo = FALSE, warning = FALSE, message = FALSE, eval = TRUE}

@@

  ggsave(filename = file.path(dir_fig, sprintf('rangemap_q1_%s.png', str_replace(tolower(spp), ' ', '_'))),
         plot = spp_plot, 
         width = 8, height = 4, dpi = 200)
}

@@

Plotting species from q2 (distribution-matched)
```{r plot_spp_from_q2, echo = FALSE, warning = FALSE, message = FALSE, eval = TRUE}

@@

  ggsave(filename = file.path(dir_fig, sprintf('rangemap_q2_%s.png', str_replace(tolower(spp), ' ', '_'))),
         plot = spp_plot, 
         width = 8, height = 4, dpi = 200)
}

```
***

@@

#Plot both maps
myTheme=rasterTheme(region=brewer.pal('Blues', n=9))

levelplot(am_sp_map,par.settings=myTheme,main='Aquamaps Dataset',colorkey=list( at=seq(0, 1063, length=15)))

levelplot(iucn_sp_map,par.settings=myTheme,main='IUCN Dataset',colorkey=list(at=seq(0, 1063, length=15)))
```

@@

hcaf <- fread(file.path(dir_anx,'raw/aquamaps_2014/tables/hcaf.csv'))%>% #bring this in just to get loiczid
          as.data.frame()%>%
            select(CsquareCode,LOICZID)%>%
              rename(loiczid=LOICZID)

all_am = am_spp_cells_big%>%
          select(SpeciesID,CsquareCode)%>%
          group_by(CsquareCode)%>%
          summarize(count=n())%>%
          as.data.frame()

all = left_join(all_am,hcaf)

@@

levelplot(all_am_map,par.settings=myTheme,main='Entire Aquamaps Dataset')
```

@@

Plotting species from q3 (area-matched)
```{r plot_spp_from_q3, echo = FALSE, warning = FALSE, message = FALSE, eval = TRUE}

  ggsave(filename = file.path(dir_fig, sprintf('rangemap_q3_%s.png', str_replace(tolower(spp), ' ', '_'))),
         plot = spp_plot, 
         width = 8, height = 4, dpi = 200)
}

Plotting species from q4 (poorly matched)
```{r plot_spp_from_q4, echo = FALSE, warning = FALSE, message = FALSE, eval = TRUE}

  ggsave(filename = file.path(dir_fig, sprintf('rangemap_q4_%s.png', str_replace(tolower(spp), ' ', '_'))),
         plot = spp_plot, 
         width = 8, height = 4, dpi = 200)
}

>>>>

@@

  # ggsave(filename = file.path(dir_fig, sprintf('rangemap_%s_%s.png', spp_quad,
  #                                              str_replace(tolower(spp), ' ', '_'))),
  #        plot = spp_plot, 
  #        width = 8, height = 4, dpi = 200)
}

@@

Plotting species from q1 (well-matched) (see data_explore_quadmaps.html for plots)
```{r plot_spp_from_q1, echo = FALSE, warning = FALSE, message = FALSE, eval = FALSE}

@@

  # ggsave(filename = file.path(dir_fig, sprintf('rangemap_q1_%s.png', str_replace(tolower(spp), ' ', '_'))),
  #        plot = spp_plot, 
  #        width = 8, height = 4, dpi = 200)
}

@@

Plotting species from q2 (distribution-matched)
```{r plot_spp_from_q2, echo = FALSE, warning = FALSE, message = FALSE, eval = FALSE}

@@

  # ggsave(filename = file.path(dir_fig, sprintf('rangemap_q2_%s.png', str_replace(tolower(spp), ' ', '_'))),
  #        plot = spp_plot, 
  #        width = 8, height = 4, dpi = 200)
}

Plotting species from q3 (area-matched)
```{r plot_spp_from_q3, echo = FALSE, warning = FALSE, message = FALSE, eval = FALSE}

  # ggsave(filename = file.path(dir_fig, sprintf('rangemap_q3_%s.png', str_replace(tolower(spp), ' ', '_'))),
  #        plot = spp_plot, 
  #        width = 8, height = 4, dpi = 200)
}

Plotting species from q4 (poorly matched)
```{r plot_spp_from_q4, echo = FALSE, warning = FALSE, message = FALSE, eval = FALSE}

  # ggsave(filename = file.path(dir_fig, sprintf('rangemap_q4_%s.png', str_replace(tolower(spp), ' ', '_'))),
  #        plot = spp_plot, 
  #        width = 8, height = 4, dpi = 200)
}

***

@@

#Plot both maps
myTheme = rasterTheme(region = brewer.pal('Blues', n = 9))

levelplot(am_sp_map, par.settings = myTheme, main = 'Aquamaps Dataset', colorkey = list( at = seq(0, 1063, length = 15)))

levelplot(iucn_sp_map, par.settings = myTheme, main = 'IUCN Dataset', colorkey = list(at = seq(0, 1063, length = 15)))
```

@@

hcaf <- fread(file.path(dir_anx, 'raw/aquamaps_2014/tables/hcaf.csv')) %>% #bring this in just to get loiczid
          as.data.frame() %>%
            select(CsquareCode, LOICZID) %>%
              rename(loiczid = LOICZID)

all_am = am_spp_cells_big %>%
          select(SpeciesID,CsquareCode) %>%
          group_by(CsquareCode) %>%
          summarize(count=n()) %>%
          as.data.frame()

all = left_join(all_am, hcaf)

@@

levelplot(all_am_map, par.settings = myTheme, main = 'Entire Aquamaps Dataset')
```

@@
